### 2023-07-22 manuscripts/Hussain-Hadah/Hussain-Hadah.tex
add elsavier manuscript

\documentclass{wptemp}
\usepackage{adjustbox}
\usepackage{dcolumn}    % aligning decimals
    \newcolumntype{d}[1]{D{.}{.}{#1}}
% *****************************************************************
% Estout LaTeX wrapper
% *****************************************************************

\usepackage{lscape}
\usepackage{threeparttablex}
\usepackage{longtable}

%%Original code developed by Jörg Weber: see
%% https://www.jwe.cc/2012/03/stata-latex-tables-estout/
%% and
%% https://www.jwe.cc/blog/

\let\estinput=\input % define a new input command so that we can still flatten the document

\newcommand{\estwide}[3]{
		\vspace{.75ex}{
			%\textsymbols% Note the added command here
			\begin{tabular*}
			{\textwidth}{@{\hskip\tabcolsep\extracolsep\fill}l*{#2}{#3}}
			\toprule
			\estinput{#1}
			\bottomrule
			\addlinespace[.75ex]
			\end{tabular*}
			}
		}

\newcommand{\estauto}[3]{
		\vspace{.75ex}{
			%\textsymbols% Note the added command here
			\begin{tabular}{l*{#2}{#3}}
			\toprule
			\estinput{#1}
			\bottomrule
			\addlinespace[.75ex]
			\end{tabular}
			}
		}

% Allow line breaks with \\ in specialcells
\newcommand{\specialcell}[2][c]{%
    \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}
}

\newcommand{\sym}[1]{\rlap{#1}}% Thanks David Carlisle

%%%%%%%%%%% End of wrapper %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% TiKz %%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{document}

\linespread{1}{\title{{\fontfamily{ptm}
\selectfont{\Large{\MakeUppercase{The Impact of Hispanic Last Names and Identity on Labor Market Outcomes}}}}}}
	\author{{\fontfamily{pbk}\selectfont\large{\textsc{Hussain Hadah}}\thanks{Department of Economics, Tulane University, 6823 St. Charles Ave., New Orleans, LA 70118, United States (e-mail: \email{hhadah@tulane.edu}).}}}
	\date{\fontfamily{pbk}\selectfont\normalsize{\textsc{\today}}}
	\maketitle

\begin{center}
\href{https://hhadah.github.io/hispanic-last-names/my_paper/Hadah-last-names.pdf}{\textcolor{green!15!black!30!blue}{\footnotesize{\textsc{Click Here to Get the Most Updated Version}}}}
\end{center}

\pagenumbering{arabic}

\begin{abstract} 
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 6 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.

\keywords{Economics of Minorities, Race, and Immigrants; Discrimination and Prejudice.}
\JEL{J71; J64}

\end{abstract}

\pagebreak
\section{Introduction}\label{sec:intro}

@@

@@

The rest of the paper is organized as follows. Section \ref{sec:data} provides an overview of the data and summary statistics of the sample. Section \ref{sec:emp_model} introduces the empirical framework. I report the results in section \ref{sec:results}. Finally, I offer a brief conclusion in section \ref{sec:con1}.

@@

The distribution of the four types of children is presented in figure \ref{fig:dist} and table \ref{tab:mat1}. The majority of the sample (95.96\%) is WW children. The second biggest group is HH, which constitutes 2.69\% of the sample. Inter-ethnic children, WH and HW, make up 1.35\% of the sample with 90,325 observations. Even though WH and HW are only 1.35\% of the sample, I have plenty of observations to carry out an analysis. The summary statistics for the children of the four types of marriages are presented in table \ref{tab:c&p1}. Children of WW marriages (column 1) do better on every measure while children of HH parents (column 4) do worse than other children on every measure.

@@

Inter-ethnic children, WH and HW, have lower educational attainment and income than WW children, but they are better than HH children. Also, WH and HW are comparable, unlike WW and HH children. These two groups are important to the analysis. Children of HW are going to be the treatment group. HW children have a Hispanic father with a Hispanic last names. At the same time, the WH children have White fathers with a non-Hispanic, or White, last names. Summary statistics of these two groups, table \ref{tab:c&p1} columns (2) and (3) can show that they are different from the children of non-inter-ethnic marriages.

@@

In panel C of table \ref{tab:c&p1}, I present the rates at which members of each group self-identify as Hispanic. \footnote{Hispanic self-identification is observed when an individual notes that they are Hispanic on the CPS questionnaire} The vast majority of HH children, 96\% for men and 97\% for women, identify as Hispanic. There is considerable attrition in Hispanic identification of inter-ethnic children. Among WH children, 74\% of men and 78\% of women identify as Hispanic. Among HW children, 83\% of men and 82\% of women identify as Hispanic. These results align with the findings of a substantial body of literature that noted this attrition among children of immigrants, especially those coming from inter-ethnic marriages \citep{duncan2017complexity, duncan2018identifying, duncan2020new, antman2020ethnic}. Finally, a small portion of WW children, 4\% of men and 5\% of women, identified as Hispanic. These 5\% of WW children are most likely third generation--- or higher--- children of immigrants. For my analysis, I dropped the WW observations who identify as Hispanic when I compare with non-Hispanic Whites.

@@

In table \ref{tab:c&p2}, I present the summary statistics for the four types and limit the sample to those that only identify as Hispanic.\footnote{Limiting the sample to those who identify as Hispanic only affects WH, HW, and HH. Members of the WW group are not affected by this restriction.} The same pattern discussed above between HH--WW and HW--WH persists. The one difference is that those who identify as Hispanic do slightly worse.

@@

I show the distribution of the four types of couples in table \ref{tab:mat2}. White husbands and White wives (WW) make up the majority of couples in the sample, 96\% (5,141,737 couples). Hispanic husbands and wives (HH) are the second largest group making up 2\% (119,749 couples) of all couples. White husbands and Hispanic wives (WH) couples are less 1\% (33,097 couples) of the sample and Hispanic husbands and White wives (HW) are also 1\% (37,847 couples).

I present the summary statistics of the four types of synthetic parents in table \ref{tab:synth}. WW couples have higher education, 12.75 years for husbands and 12.47 for wives. As a household, WW couples have 25.22 years of schooling. Additionally, the log total family income for a WW household is 10.72 and have 3.77 children. Husbands in HH marriages have 8.64 years of education, while women have 8.49 years of schooling. As a household, HH couples have 17.13 years of education, log total family income of 10.27, and have 4.23 children.

@@

In columns 5 and 6 of table \ref{tab:synth}, I report the differences in means between HH-WW households and HW-WH households. An HH Hispanic husband attained 4.11 fewer years of education than a WW husband. While an HH wife acquired 3.98 fewer years of schooling than a White WW wife. The total educational difference between HH and WW households equals 8.09 years of education. The educational differences between HW and WH are less severe than those between HH and WW. A Hispanic husband in intermarriage attained 1.52 fewer years of schooling than a White husband in intermarriage. A White wife in intermarriage attained 0.70 years of education, more than a Hispanic wife in intermarriage. The difference in total years of education between HW and WH households is 0.81, which is an 90\% decrease from the HH--WW gap. The total family income of an HH household is 45\% lower than a WW household, while the total family income of an HW household is 10\% lower than a WH household. These differences show that couples that intermarry are better and different than those that do not.

@@

\subsection{Estimating the effect of having a Hispanic last name}

@@

The coefficients of interest from equation \ref{eq:iden} are $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$. The coefficients $\beta_{1}$ and $\beta_{3}$ capture the effects of Spanish-sounding last names for $HW_{ist}$ that identify as Hispanic \textit{versus} those who do not.

\section{Results}\label{sec:results}

In this section, I present the results from estimating the two specifications in equations \ref{eq:1a} and \ref{eq:iden}. The results are shown in tables \ref{tab:lastnamereg} and \ref{tab:identreg}. All estimations are done on a sample of White, native-born men between the ages of 25 and 40 employed for full-time full-year (FTFY) and are wage and salary workers.

@@

I provide the results to the estimation of equation \ref{eq:1a} in table \ref{tab:lastnamereg}. The sample in this analysis includes full-time, full-year, and wage and salary men, and I control for hours worked and age and include year fixed effects (FE). I also restrict the sample to children of HW and WH (omitted) parents. Column one in table \ref{tab:lastnamereg} is the results without controlling for education. Overall, an inter-ethnic with a Hispanic last name earns 6 percentage points less than an inter-ethnic with a White last name. This gap, however, could be entirely explained by educational differences. An inter-ethnic with a Hispanic last name earns 6 percentage points less than an inter-ethnic with a White last name, but the result is statistically insignificant.

I provide the results to the estimation of equation \ref{eq:iden} in table \ref{tab:identreg}. The sample in this analysis includes full-time, full-year, and wage and salary men, and I control for hours worked and age and include year fixed effects (FE). I also restrict the sample to children of HW and WH parents. The omitted group is children of WH parents that do not identify as Hispanic. Column one in table \ref{tab:identreg} is the results without controlling for education. An inter-ethnic $HW_{ist}$ that identifies as Hispanic \textit{versus} $HW_{ist}$ who do not---i.e. $HW_{ist} + HW_{ist} \cdot Hispanic_i$---earns 6 percentage points less than an inter-ethnic that does not, but the result could be entirely explained by educational differences.

@@

% \nocite{*}
\pagebreak
\bibliography{bibliography}
\newpage
\pagebreak
\begin{appendices}

\section{Figures}\label{appendix:figures}

\begin{center}
\begin{figure}[h!]
\caption{Inter-racial marriages as a percent of all marriages \\
 in the United States from 1995 to 2020.}
\includegraphics[width=\textwidth]{interracialovertime.png} 
\label{fig:3}
\end{figure}
\end{center}

\newpage

\begin{center}
\begin{figure}[h!]
\caption{Distribution of the four types of children.}
\includegraphics[width=\textwidth]{PirChart2.png} 
\label{fig:dist}
\end{figure}
\end{center}

\newpage

\begin{figure}[h!]
\centering
\caption{Chart explaining which synthetic parents and children and when we observe them.}
\begin{tikzpicture}[node distance =2cm]
\node (start) [startstop] {Synthetic Parents: Observed in 1960 to 2000. $25 \leq age \leq 40$, White, with kids};

\draw [arrow] (start) -- (pro1);
\end{tikzpicture}
\label{flowchart1}
\end{figure}

\newpage

\section{tables}\label{appendix:tables}

\input{tables/tab01-observations-by-parents}

\newpage

\input{tables/tab02-observations-by-couple}

\newpage

\input{tables/tab03b-summary-stats}

\newpage

\input{tables/tab03a-summary-stats}

\newpage

% \input{tables/tab03a-summary-stats-mex}

% \newpage

% \input{tables/tab03a-summary-stats-nonmex}

% \newpage

\input{tables/tab04-summary-stats}

\newpage

\input{tables/tab05-regression}

\newpage

\input{tables/tab06-regression}

\end{appendices}

>>>>

%%
%% Copyright 2019-2021 Elsevier Ltd
%%
%% This file is part of the 'CAS Bundle'.
%% --------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'CAS Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for cas-sc documentclass for
%% single column output.

\documentclass[a4paper,fleqn]{cas-sc}

% If the frontmatter runs over more than one page
% use the longmktitle option.

%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}

%\usepackage[numbers]{natbib}
\usepackage[authoryear]{natbib}
%\usepackage[authoryear,longnamesfirst]{natbib}

%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
%%%

% Uncomment and use as if needed
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newdefinition{rmk}{Remark}
%\newproof{pf}{Proof}
%\newproof{pot}{Proof of Theorem \ref{thm}}

\usepackage{lscape}
\usepackage{threeparttablex}
\usepackage{longtable}
% Allow line breaks with \\ in specialcells
\newcommand{\specialcell}[2][c]{%
    \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}
}

\usepackage{dcolumn}    % aligning decimals
    \newcolumntype{d}[1]{D{.}{.}{#1}}

\usepackage{siunitx}
%%%%%%%%%%% TiKz %%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\tikzstyle{arrow} = [thick,->,>=stealth]
\begin{document}

\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

% Short title
\shorttitle{The impact of Hispanic last names and identity on labor market outcomes}

% Short author
\shortauthors{H. Hadah}

% Main title of the paper
\title [mode = title]{The impact of Hispanic last names and identity on labor market outcomes}

\author[]{Hussain Hadah}[orcid=https://orcid.org/0000-0002-8705-6386]
\ead{hhadah@tulane.edu}

\affiliation[]{organization={Department of Economics, Tulane University},
            addressline={6823 St. Charles Ave.},
            city={New Orleans},
%          citysep={}, % Uncomment if no comma needed between city and postcode
            postcode={70118},
            state={LA},
            country={United States}}

\begin{abstract}
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 6 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.
\end{abstract}

\begin{keywords}
 Economics of Minorities, Race, and Immigrants\sep Discrimination and Prejudice\\
 \JEL{J71\sep J64}
\end{keywords}

\maketitle

\section{Introduction}\label{sec:intro}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.25]{Fig/interracialovertime.png}
\caption{Inter-racial marriages as a percent of all marriagesin the United States from 1995 to 2020.}
\label{fig:3}
\end{figure}

@@

The rest of the paper is organized as follows. Section \ref{sec:data} provides an overview of the data and summary statistics of the sample. Section \ref{sec:emp_model} introduces the empirical framework. I report the results in Section \ref{sec:results}. Finally, I offer a brief conclusion in Section \ref{sec:con1}.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.4]{Fig/PirChart2.png}
\caption{Distribution of the four types of children.}
\label{fig:dist}
\end{figure}

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance =2cm]
\node (start) [startstop] {Synthetic Parents: Observed in 1960 to 2000. $25 \leq age \leq 40$, White, with kids};

\draw [arrow] (start) -- (pro1);
\end{tikzpicture}
\caption{Chart explaining which synthetic parents and children and when we observe them.}
\label{flowchart1}
\end{figure}

The distribution of the four types of children is presented in Fig. \ref{fig:dist} and Table \ref{tab:mat1}. The majority of the sample (95.96\%) is WW children. The second biggest group is HH, which constitutes 2.69\% of the sample. Inter-ethnic children, WH and HW, make up 1.35\% of the sample with 90,325 observations. Even though WH and HW are only 1.35\% of the sample, I have plenty of observations to carry out an analysis. The summary statistics for the children of the four types of marriages are presented in Table \ref{tab:c&p1}. Children of WW marriages (column 1) do better on every measure while children of HH parents (column 4) do worse than other children on every measure.

%table1
\input{tables/tab01-observations-by-parents}
%table2
\input{tables/tab02-observations-by-couple}

@@

Inter-ethnic children, WH and HW, have lower educational attainment and income than WW children, but they are better than HH children. Also, WH and HW are comparable, unlike WW and HH children. These two groups are important to the analysis. Children of HW are going to be the treatment group. HW children have a Hispanic father with a Hispanic last names. At the same time, the WH children have White fathers with a non-Hispanic, or White, last names. Summary statistics of these two groups, Table \ref{tab:c&p1} columns (2) and (3) can show that they are different from the children of non-inter-ethnic marriages.

%table3
\input{tables/tab03b-summary-stats}

@@

In panel C of Table \ref{tab:c&p1}, I present the rates at which members of each group self-identify as Hispanic. \footnote{Hispanic self-identification is observed when an individual notes that they are Hispanic on the CPS questionnaire} The vast majority of HH children, 96\% for men and 97\% for women, identify as Hispanic. There is considerable attrition in Hispanic identification of inter-ethnic children. Among WH children, 74\% of men and 78\% of women identify as Hispanic. Among HW children, 83\% of men and 82\% of women identify as Hispanic. These results align with the findings of a substantial body of literature that noted this attrition among children of immigrants, especially those coming from inter-ethnic marriages \citep{duncan2017complexity, duncan2018identifying, duncan2020new, antman2020ethnic}. Finally, a small portion of WW children, 4\% of men and 5\% of women, identified as Hispanic. These 5\% of WW children are most likely third generation--- or higher--- children of immigrants. For my analysis, I dropped the WW observations who identify as Hispanic when I compare with non-Hispanic Whites.

@@

In Table \ref{tab:c&p2}, I present the summary statistics for the four types and limit the sample to those that only identify as Hispanic.\footnote{Limiting the sample to those who identify as Hispanic only affects WH, HW, and HH. Members of the WW group are not affected by this restriction.} The same pattern discussed above between HH--WW and HW--WH persists. The one difference is that those who identify as Hispanic do slightly worse.

%table4
\input{tables/tab03a-summary-stats}

@@

%table5
\input{tables/tab04-summary-stats}

I show the distribution of the four types of couples in Table \ref{tab:mat2}. White husbands and White wives (WW) make up the majority of couples in the sample, 96\% (5,141,737 couples). Hispanic husbands and wives (HH) are the second largest group making up 2\% (119,749 couples) of all couples. White husbands and Hispanic wives (WH) couples are less 1\% (33,097 couples) of the sample and Hispanic husbands and White wives (HW) are also 1\% (37,847 couples).

I present the summary statistics of the four types of synthetic parents in Table \ref{tab:synth}. WW couples have higher education, 12.75 years for husbands and 12.47 for wives. As a household, WW couples have 25.22 years of schooling. Additionally, the log total family income for a WW household is 10.72 and have 3.77 children. Husbands in HH marriages have 8.64 years of education, while women have 8.49 years of schooling. As a household, HH couples have 17.13 years of education, log total family income of 10.27, and have 4.23 children.

@@

In columns 5 and 6 of Table \ref{tab:synth}, I report the differences in means between HH-WW households and HW-WH households. An HH Hispanic husband attained 4.11 fewer years of education than a WW husband. While an HH wife acquired 3.98 fewer years of schooling than a White WW wife. The total educational difference between HH and WW households equals 8.09 years of education. The educational differences between HW and WH are less severe than those between HH and WW. A Hispanic husband in intermarriage attained 1.52 fewer years of schooling than a White husband in intermarriage. A White wife in intermarriage attained 0.70 years of education, more than a Hispanic wife in intermarriage. The difference in total years of education between HW and WH households is 0.81, which is an 90\% decrease from the HH--WW gap. The total family income of an HH household is 45\% lower than a WW household, while the total family income of an HW household is 10\% lower than a WH household. These differences show that couples that intermarry are better and different than those that do not.

@@

%table6
\input{tables/tab05-regression}
\subsection{Estimating the effect of having a Hispanic last name}

@@

The coefficients of interest from Eq. \eqref{eq:iden} are $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$. The coefficients $\beta_{1}$ and $\beta_{3}$ capture the effects of Spanish-sounding last names for $HW_{ist}$ that identify as Hispanic \textit{versus} those who do not.
%table7
\input{tables/tab06-regression}
\section{Results}\label{sec:results}

In this section, I present the results from estimating the two specifications in Eqs. \eqref{eq:1a} and \eqref{eq:iden}. The results are shown in Tables \ref{tab:lastnamereg} and \ref{tab:identreg}. All estimations are done on a sample of White, native-born men between the ages of 25 and 40 employed for full-time full-year (FTFY) and are wage and salary workers.

@@

I provide the results to the estimation of Eq. \eqref{eq:1a} in Table \ref{tab:lastnamereg}. The sample in this analysis includes full-time, full-year, and wage and salary men, and I control for hours worked and age and include year fixed effects (FE). I also restrict the sample to children of HW and WH (omitted) parents. Column one in Table \ref{tab:lastnamereg} is the results without controlling for education. Overall, an inter-ethnic with a Hispanic last name earns 6 percentage points less than an inter-ethnic with a White last name. This gap, however, could be entirely explained by educational differences. An inter-ethnic with a Hispanic last name earns 6 percentage points less than an inter-ethnic with a White last name, but the result is statistically insignificant.

I provide the results to the estimation of Eq. \eqref{eq:iden} in Table \ref{tab:identreg}. The sample in this analysis includes full-time, full-year, and wage and salary men, and I control for hours worked and age and include year fixed effects (FE). I also restrict the sample to children of HW and WH parents. The omitted group is children of WH parents that do not identify as Hispanic. Column one in Table \ref{tab:identreg} is the results without controlling for education. An inter-ethnic $HW_{ist}$ that identifies as Hispanic \textit{versus} $HW_{ist}$ who do not---i.e. $HW_{ist} + HW_{ist} \cdot Hispanic_i$---earns 6 percentage points less than an inter-ethnic that does not, but the result could be entirely explained by educational differences.

@@

\bibliographystyle{cas-model2-names}
\bibliography{bibliography}

### 2023-07-22 manuscripts/Hussain-Hadah/tables/tab02-observations-by-couple.tex
add elsavier manuscript

\begin{table}[H]

\caption{Couples' Type \label{tab:mat2}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Couples Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Husband \\ White Wife} & \specialcell{White Husband \\ Hispanic Wife} & \specialcell{Hispanic Husband \\ White Wife} & \specialcell{Hispanic Husband \\ Hispanic Wife}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{1,286,731\\0.97} & \specialcell{7,178\\0.01} & \specialcell{7,606\\0.01} & \specialcell{20,911\\0.02}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: 1970-1990 Census
\item[2] The sample includes Whites, who are married, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[t]
\caption{Couples' Type \label{tab:mat2}}
%\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Couples Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Husband \\ White Wife} & \specialcell{White Husband \\ Hispanic Wife} & \specialcell{Hispanic Husband \\ White Wife} & \specialcell{Hispanic Husband \\ Hispanic Wife}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{5,141,737\\0.96} & \specialcell{33,097\\0.01} & \specialcell{37,847\\0.01} & \specialcell{119,749\\0.02}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: 1960-2000 Census
\item[2] The sample includes Whites, who are married, with kids, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White if she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}
%}
\end{table}

### 2023-07-22 manuscripts/Hussain-Hadah/tables/tab03a-summary-stats-mex.tex
add elsavier manuscript

\caption{Summary statistics of synthetic parents by couple type \label{tab:synth}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
Husband's education (Total Years) & \specialcell{12.75\\(0.61)} & \specialcell{11.77\\(1.87)} & \specialcell{10.25\\(2.44)} & \specialcell{8.64\\(2.01)} & \specialcell{-4.11***\\(0.00)} & \specialcell{-1.52***\\(0.00)}\\
Wife's education (Total Years) & \specialcell{12.47\\(0.56)} & \specialcell{10.40\\(2.23)} & \specialcell{11.11\\(1.75)} & \specialcell{8.49\\(1.92)} & \specialcell{-3.98***\\(0.00)} & \specialcell{0.70***\\(0.00)}\\
Total Household seducation (Total Years) & \specialcell{25.22\\(1.17)} & \specialcell{22.17\\(4.05)} & \specialcell{21.36\\(4.10)} & \specialcell{17.13\\(3.88)} & \specialcell{-8.09***\\(0.00)} & \specialcell{-0.81***\\(0.01)}\\
Log Total Family Income & \specialcell{10.72\\(0.09)} & \specialcell{10.55\\(0.26)} & \specialcell{10.46\\(0.27)} & \specialcell{10.27\\(0.21)} & \specialcell{-0.45***\\(0.00)} & \specialcell{-0.10***\\(0.00)}\\
Fertility & \specialcell{3.77\\(0.40)} & \specialcell{3.98\\(0.71)} & \specialcell{4.15\\(0.79)} & \specialcell{4.23\\(0.64)} & \specialcell{0.46***\\(0.00)} & \specialcell{0.17***\\(0.00)}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: The 1950-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens who are also White, between the ages of 25 and 40, and have kids. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Summary statistics of synthetic parents by couple type (Mexican Hispanics) \label{tab:synthmex}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
Husband's education (Total Years) & \specialcell{12.75\\(0.61)} & \specialcell{10.80\\(1.41)} & \specialcell{9.14\\(1.52)} & \specialcell{7.85\\(1.24)} & \specialcell{-4.90***\\(0.00)} & \specialcell{-1.65***\\(0.01)}\\
Wife's education (Total Years) & \specialcell{12.47\\(0.56)} & \specialcell{9.27\\(1.71)} & \specialcell{10.46\\(1.32)} & \specialcell{7.80\\(1.36)} & \specialcell{-4.67***\\(0.00)} & \specialcell{1.19***\\(0.00)}\\
Total Household education (Total Years) & \specialcell{25.22\\(1.17)} & \specialcell{20.06\\(3.09)} & \specialcell{19.60\\(2.80)} & \specialcell{15.65\\(2.60)} & \specialcell{-9.57***\\(0.00)} & \specialcell{-0.47**\\(0.01)}\\
Log Total Family Income & \specialcell{10.72\\(0.09)} & \specialcell{10.42\\(0.14)} & \specialcell{10.33\\(0.12)} & \specialcell{10.20\\(0.07)} & \specialcell{-0.52***\\(0.00)} & \specialcell{-0.09***\\(0.00)}\\
Fertility & \specialcell{3.77\\(0.40)} & \specialcell{4.26\\(0.64)} & \specialcell{4.33\\(0.64)} & \specialcell{4.46\\(0.49)} & \specialcell{0.69***\\(0.00)} & \specialcell{0.07***\\(0.00)}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: The 1960-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens who are also White, between the ages of 25 and 40, and have kids. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Mexico. A parent is White if they were born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}
